FEM Model Analysis

### 2021-02-17 FEM_R/model_analysis_core.Rmd
Creating copies of some files for the core model, including a new covar_definitions file with stripped back right hand variables

baseline <- read_dta('ELSA_Baseline/ELSA_Baseline_summary.dta')

@@

```{r echo = FALSE}
cohort <- read_dta('ELSA_cohort/ELSA_cohort_summary.dta')

@@

```{r}
FEM_base <- read_dta('ELSA_Baseline/ELSA_Baseline_summary.dta')

>>>>

baseline <- read_dta('ELSA_core_base/ELSA_core_base_summary.dta')

@@

```{r echo = FALSE}
cohort <- read_dta('ELSA_core_cohort/ELSA_core_cohort_summary.dta')

@@

```{r}
FEM_base <- read_dta('ELSA_core_base/ELSA_core_base_summary.dta')
